 \documentclass[11pt]{article}

\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\begin{document}

\textbf{NAMES: MATANDA KELVIN}


\textbf{REGISTRATION NUMBER: 15/U/7444/EVE}


\textbf{STUNDENT NUMBER: 215004160}


\textbf{CONCEPT PAPER}\\



\begin{large}\textbf{PROBLEMS FACED RUNNING LOCAL RETAIL SHOPS.}\end{large}\\

\section{INTRODUCTION}
\begin{enumerate}
\item BACKGROUND TO PROBLEM\\
Small retail shops have often raised concern when it comes to the profits that come out of them as a business.
 Often people suggest that maybe they are not the best of options when one considers to start up a small business.

\item OBJECTIVES\\
Find out the potential problems that come with starting up a small retail shop and how to make the best of it.
To try and bring awareness To Whom It May Concern and give a person some sort of first-hand information from the
 real field that may act as a pivot or centre of focus while they decide to undertake a business of the sort.


\item SCOPE\\
The research is set to take about three to four days.
The research is set to cover the challenges that come with having a retail business.
 The research may also cover the upside of the business. 

\item SIGNIFICANCE\\
I think it is important for people who have interest in taking up such a slow earning business to know what to expect.
Getting to know the problems that most retailers are going through can help the aspirants of the business prepare and
 maybe find better approaches to make the business as fruitful as possible. 


\end{enumerate}•

\section{METHODOLOGY}The method for this research is by interview. 
The method was implemented using forms that recorded and stored information in a dedicated server. 


\section{REFERENCES}
https://matanda22kelvin.appspot.com/Aggregate.html



\end{document}